\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1.2in]{geometry}
\usepackage{hyperref}

\usepackage{listings}
\usepackage{xcolor}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=mystyle}

\usepackage{tikz}
\usetikzlibrary{positioning}

\usepackage{natbib}
\usepackage{graphicx}
\usepackage{amsmath}

\title{\vspace{-2 cm}Federal University of Ouro Preto \\ PCC104 - Project and Analysis of Algorithms \\ Divide and Conquer}
\author{Prof. Rodrigo Silva}
%
\date{}

\begin{document}

\maketitle

\section{Recommended Reading}

\begin{itemize}
    \item Chapter 4 - \textit{Introduction to the Design and Analysis of Algorithms (3rd Edition)} by Anany Levitin
    \item Book - \textit{Problem Solving with Algorithms and Data Structures using C++} (available at: \url{https://runestone.academy/runestone/books/published/cppds/index.html#})
\end{itemize}

\section{Practical Activities}

\begin{enumerate}
    \item Implement the \textit{Insertion Sort} algorithm.
    %\item Implement the topological sort algorithm.
    %\item Implement the Johnson-Trotter algorithm to generate permutations.
    %\item Implement the \textit{LexicographicPermute} method presented in the textbook.
    %\item Implement an algorithm that, given a set of elements, generates all its subsets.
    \item Implement the binary search algorithm.
    \item Implement an algorithm for the \textit{fake coin problem}.
    \item Implement the \textit{interpolation search} method.
    %\item Implement an algorithm for calculating the median without sorting the set of numbers.
    %\item Implement the \textit{binary search tree} data structure and the methods for searching and inserting.
    % https://hub.packtpub.com/binary-search-tree-tutorial/
\end{enumerate}

For each implementation, present the time complexity analysis of the algorithm. This analysis should include:

\begin{itemize}
    \item A mathematical expression defining the cost of the algorithm (recurrence relation for recursive algorithms or summation for iterative ones).
    \item Calculation of the cost function.
    \item Indication of the efficiency class ($O$ or $\Theta$). The indication of the class should be justified. You can prove it using the definition, the limit, the master theorem, or results demonstrated in class.
\end{itemize}

%
\end{document}
