\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1.2in]{geometry}
\usepackage{hyperref}

\usepackage{listings}
\usepackage{xcolor}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=mystyle}


\usepackage{tikz}
\usetikzlibrary{positioning}

\usepackage{natbib}
\usepackage{graphicx}
\usepackage{amsmath}

\title{\vspace{-2 cm}Federal University of Ouro Preto \\ PCC104 - Design and Analysis of Algorithms \\ Divide and Conquer}
\author{Prof. Rodrigo Silva}
%\date{}

\begin{document}

\maketitle

\section*{Instructions}

\begin{itemize}
    \item For each set of algorithms, the student must choose one.
    \item The student must create a public GitHub repository with all the developed codes.
    \item For each implementation, the student must:
    \begin{itemize}
        \item Present 3 test cases.
        \item Be prepared to develop the cost analysis.
        \item Be prepared to answer questions about their own code, the algorithm, and the problem the algorithm solves.
    \end{itemize}
    \item The interviews will take place between 
\end{itemize}

\section{Set 1 - Divide and Conquer}
Chapter 5 - \textit{Introduction to the Design and Analysis of Algorithms (3rd Edition)} by Anany Levitin

\begin{enumerate}
    \item Implement the MergeSort algorithm.
    \item Implement the QuickSort algorithm.
    \item Implement a binary tree and its traversal algorithms:
    \begin{enumerate}
        \item Pre-order
        \item Post-order
        \item In-order
    \end{enumerate}
\end{enumerate}

\section{Set 2 - Dynamic Programming}
Chapter 8 - \textit{Introduction to the Design and Analysis of Algorithms (3rd Edition)} by Anany Levitin

\begin{enumerate}
    \item Implement the two dynamic programming algorithms for the knapsack problem. (Section 8.2)
\end{enumerate}

\section{Set 3 - Greedy Algorithms}
Chapter 9 - \textit{Introduction to the Design and Analysis of Algorithms (3rd Edition)} by Anany Levitin

\begin{enumerate}
    \item Implement Prim's algorithm.
    \item Implement Kruskal's algorithm.
    \item Implement Dijkstra's algorithm.
\end{enumerate}

\section{Set 4 - Backtracking}
Section 12.1 - \textit{Introduction to the Design and Analysis of Algorithms (3rd Edition)} by Anany Levitin

\begin{enumerate}
    \item Implement a backtracking algorithm for the n-queens problem.
    \item Implement a backtracking algorithm for the \textit{subset-sum} problem.
\end{enumerate}

\section{Set 5 - Branch and Bound}
Section 12.2 - \textit{Introduction to the Design and Analysis of Algorithms (3rd Edition)} by Anany Levitin

\begin{enumerate}
    \item Implement a branch and bound algorithm for the knapsack problem.
    \item Implement a branch and bound algorithm for the traveling salesman problem.  
\end{enumerate}

%\footnotetext{Book - \textit{Introduction to the Design and Analysis of Algorithms (3rd Edition)}}

%\bibliographystyle{plain}
%\bibliography{references}
\end{document}
